%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {Information and Communication Technology for Development (ICTD) Lab at Paul G. Allen School (CSE)} % Organization
    {Graduate Researcher \& Undergraduate Researcher} % Job title
    {March 2019 - Present} % Date
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Applies mixed-methods research to analyze how the air pollution impacts motorcycle-taxi Grab workers' strategies and income in Southeast Asia (in partnership with Grab Holding Inc.). To appear in CSCW 2024.
        }
        \item {
          Enhance sensor technology, engage with novel at-risk demographics, and develop comprehensive policy documentation to highlight the impact of urban air pollution in on vulnerable populations in Thailand. Explore potential optimizations, such as adjusting work schedules, while acknowledging existing constraints.
        }
        \item {
          Collaborate in community outreach, equipment deployment, and troubleshooting on the open-sourced Community Cellular (LTE) Network project to bring affordable high-speed connectivity to lower-income neighborhoods in South Seattle and Tacoma area.
        }  
        \item{
            \href{https://github.com/innoobijr/cse-550-finalproject-mtunzi}{\textit{mtunzi}}, a system for software-defined network access control and captive networking aimed toward the networking needs of small WISPs and community network operators.
        }
        \item {
          Analyze the impact of COVID-19 on the Community Cellular Networks's internet traffic and transactions in Bokondini, Indonesia. \href{https://dl.acm.org/doi/10.1145/3460112.3472311}{\textit{(ACM COMPASS'21)}}
        }
         % \item {
        %   Test and analyze internet packets to quantify how various VoIP services perform under constrained internet conditions, such as high latency, by tracing traffic in Wireshark to develop a reliable VoIP service for constrained-resources area to improve community connectivity in the future.
        % }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {School of Engineering and Technology (UWT) } % Organization
    {} % Job title
    {} % Date
    {} 
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Interpret decision making behind Deep Learning models and decompress in order to have them operate in IoT devices efficiently, such as mobiles and tablets, to detect and block Domain Generation Algorithm (DGA) malwares with Infobox company under supervision of Prof. Juhua Hu.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Aeronautical Radio of Thailand at Bangkok Thailand} % Organization
    {Data Scientist} % Job title
    {October 2023 - Present} % Date
    {} 
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Contribute to strategic planning and implementation in the Air Traffic Flow Management (ATFM) team to optimize air traffic flow, ensure a balance between demand and capacity, and aid in reducing pollution emissions and optimizing costs amidst growing traffic.
        } 
        \item {Provide strategic advice and planning for the establishment of a Data Innovation Center, guiding the transformation of the company into a data-driven organization.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DOKK1 at Århus, Denmark} % Organization
    {Research Intern for Aarhus City Lab} % Job title
    {May 2022 - July 2022} % Date
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Applied Data Science practices analyzing the impact of cruise emissions and used Deep Learning for time series forecasting on the air quality of the second largest city of Denmark, Århus.
        }
        \item {
          This work is a collaboration with the Aarhus City Lab team, ITK department at DOKK1 (Århus, Denmark). A media coverage for the work: \href{https://itk.aarhus.dk/nyheder/projektnyheder/krydstogtskibe/cruise-ships/}{itk.aarhus.dk/nyheder/projektnyheder/krydstogtskibe/cruise-ships/}. More information, please visit \href{https://github.com/nussarafirn/aarhus-aqi}{github.com/nussarafirn/aarhus-aqi}. 
        }
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Paul G. Allen School of Computer Science \& Engineering} % Organization
    {Graduate  \& Undergraduate Teaching Assistant} % Job title
    {September 2020 - Present} % Date
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
           Assist Prof. Jeffrey Heer and  Prof. Leilani Battle with lesson plans for the \textit{\href{https://courses.cs.washington.edu/courses/cse442/22au/}{Data Visualization}} class. Instructing the class requires TAs to be proficient in using D3.js, web programming, Tableau, and observable notebooks.  Other tasks includes but not limited to holding office hours, instructing small groups of students, and providing feedback/help on assignments for classes of 120 students.
        }
      \end{cvitems}
    }
                % ----------------------------
    \cventry
    {School of Engineering and Technology (UWT)} %; Organization
    {} % Job title
    {} % Date
    {} 
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
            Teach materials and construct exercises for Data Structures, Discrete Math, and Object-Oriented Programming classes.
        }
        % \item {
        %   Establish and maintain communication with departmental faculties by being an intermediary between students and professors to help gather feedback for the course and attend weekly staffs meetings. 
        % }
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Information School at University of Washington} % Organization
    {Undergraduate Tutor} % Job title
    {September 2019 - February 2020} % Date
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Teach students one-on-one with more than 200 students especially disadvantaged and limited coding experienced students and work collaboratively with iSchool professors to improve contents for Intro to Data Science, Web development, Databases and Server-Side Development course.
        }
        % \item {
        %   Teach students one-on-one with more than 200 students especially disadvantaged and limited coding experienced students, answer questions, hold office hours both online and on-campus, and work collaboratively with iSchool professors to improve the course contents.
        % }
        % \item {
        %   Support and tutor students on technical classes such as, Intro to Data Science,Web development, Databases and Server-Side Development.
        % }
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
     {Aeronautical Radio of Thailand at Bangkok Thailand} % Organization
     {Data Science Intern} % Job title
     {July 2018 - August 2018} % date
     {} % 
     {
      \begin{cvitems} % Description(s) of tasks/responsibilities
         \item {
            Collaboratively working on optimizing airspace usage with data scientists and engineers in Air Traffic Flow Management (ATFM) Team to balance the air traffic demand of Thai airspace capacity.
         }
         \item {
            Analyze, forecast, and visualize the possible delays on each routes on over millions flight data using data mining and visualization skills and various tools including but not limited to Tableau and advanced Excel formulae.
         }
         \item {
            Successfully able to identify congested routes and the causes of delay, which have been further handled by the team accordingly.
         }
      \end{cvitems}
     }

%---------------------------------------------------------
   \cventry
     {Thai Students Association (ThaiSA) at University of Washington} % Organization
     {ThaiSA Vice President} % Job title
     {June 2018 - June 2019} % date
     {} % Date(s)
     {
       \begin{cvitems} % Description(s) of tasks/responsibilities
         \item {Organize 12 Thai cultural events with more than a thousand attendees, delegate and follow up undertaken duties along with support about 300 Thai Student community for their cultural and academic adaptation. More information about the events please visit \href{http://tinyurl.com/thaisauw}{http://tinyurl.com/thaisauw}}
       \end{cvitems}
     }

%---------------------------------------------------------
\end{cventries}
